\section{Motivation}
\label{cp5:motivation}


When provided with a set of artifacts that potentially contain information relevant to their task,
software developers must inspect the artifact's content and locate the portion of the text that might be relevant to the task-at-hand. 
Some of the artifacts inspected are short enough that a developer can find if they contain any helpful information at a quick glance.
Some others are lengthy~\cite{Rastkar2013t} and factors such
as high time pressure or
the need to meet deadlines~\cite{meyer2019}
may lead a developer to quickly skim the document
in an attempt to find any of the text that is relevant to their task~\cite{Starke2009},
what Robillard and Chhetri summarize as the information \textit{filtering problem}:

\smallskip
\begin{bluequote}
    \textit{The burden  of having to sit through large amounts of irrelevant text, e.g., because of legacy information, boilerplate text, or because the text is intended for a reader other than the developer who is currently inspecting the artifact}~\cite{Robillard2015}
\end{bluequote}



As unfruitful readings/skimming can 
cause a developer to abandon an artifact that could otherwise contain information  helpful to the developer's task~\cite{Brandt2009a, Starke2009},
several studies have proposed automatic approaches to assist this activity. 
These approaches leverage textual cues as well as an artifact's meta-data and, ultimately, they have the goal of surfacing 
the most important information in a document, e.g., highlighting the text identified as relevant so that a developer can quickly 
locate it.


As examples of approaches, Xu et al.~\cite{Xu2017} and Ponzanelli et al.~\cite{Ponzanelli2015}
argue that words that appear in a task description and also in sentences within an artifact serve to automatically identify information relevant to a task.
In turn, Silva et al.~\cite{silva2019} discuss that 
there is a lexical gap between a task description and the information associated 
with the solution for that task, which lead them to identify
relevant sentences based on word meanings.
In a similar vein, Di Sorbo et al. suggest that relevant information might be identifiable 
according to the text's purpose, such as if it details a feature request, a problem, a solution proposal and others~\cite{Sorbo2015}.


Although effective, the cues used to automatically identify text relevant to a software task in the aforementioned studies have focused on specific tasks (\red{example + ref}) and artifact types (\red{example + ref}).
Therefore, the question of whether these cues can identify relevant text across a wider range of artifact types and tasks remains open. 



As a first step towards answering this question, we set out to investigate:


\begin{enumerate}
    \item \textit{How accurately can lexical properties identify text deemed relevant to a task?}
    We assess to what extent can a lexical similarity approach automatically identify text relevant to a software task.
    We use lexical similarity as a baseline since both our card sorting analysis (\red{Section~\ref{aaa}}) and related work~\cite{Ko2006a, Freund2015} show
    that developers often use keyword-matching as a simple and quick search strategy to locate relevant information in a software artifact.


    \item \textit{How accurately can word semantics identify text deemed relevant to a task?}
    Guided by studies that discuss there are lexical gaps between a task description and the text related to that task's solution~\cite{silva2019, Huang2018, Ye2016},
    we ask if we can better identify text relevant to a software task by semantically matching the text in a task description and the text within an artifact.
    To answer this question, we investigate both a word semantics similarity approach and also state-of-the-art language models~\cite{Devlin2018Bert}.

    
    \item \textit{Does the relevance of a sentence depend on the sentence's meaning?}
    Our study on characterizing task-relevant text has show that text deemed relevant often contains semantic frames describing 
     required events, obligations, actions evoking system calls, etc (\red{Section~\ref{aaa}}).
    Given how these frames capture key factors used to understand a sentence's meaning
    and also their prominence in relevant text, 
    we assess if semantic frames help to filter task-relevant text.
\end{enumerate}


% of the answers from 20 participants
%     describing their strategies to find relevant information in 6 software tasks






% When skimming through an artifact's content, a series of intrinsic and extrinsic factors~\cite{Freund2015} 
% serve as indicators of the relevance of the text to the developer's task.
% For example, a code element that is mentioned in a task description 
% and that also appears in a sentence may lead 
% the developer to inspect the sentence more carefully and is an example of an extrinsic factor (i.e., shared keywords).
% The developer's familiarity with the document's structure
% may also guide her to skip certain parts of its content while focusing her attention to others and is 
% an example of an intrinsic factor (i.e., the developer's experience reading a certain type of artifact).





% As Table~\ref{tbl:text-properties-references} shows, many studies have 
% provided possible factors that guide the automatic identification of text relevant to a particular task.
% These factors are used in automatic approaches that help a developer in identifying parts of an artifact worthy of their attention.
% As an example, Krec uses the presence of code elements in a sentence to identify 
% text that programmers cannot afford to ignore when using an API~\cite{Robillard2015}, 
% e.g., ``\textit{Use \hl{getName} to get the logical name of the font}''.
% As another example, Sara and Treude argue that relevant text is often found in sentences
% with usage conditions~\cite{nadi2020}, 
% e.g., ``\textit{\hl{If} the permission you need to add isn't listed under the normal permissions, you'll need to deal with Runtime Permissions}''.


% \input{sections/cp5/tbl-text-properties}



% While the factors outlined in Table~\ref{tbl:text-properties-references} rely on 
% syntactic properties, we hypothesize that one can determine the relevancy of a sentence based on its semantics. 
% More specifically, our study characterizing task-relevant text has shown that certain frames---identifiable through frame semantics~\cite{fillmore1976frame}---are more prominent in sentences deemed as relevant.
% For example, in the sentence about the ``\textit{getName}'' method,
% we can identify frames detailing \texttt{using} the method to achieve a \texttt{goal}:

% \input{sections/cp5/frame-example}


% The \texttt{Using} frame is one of the frames observed in annotations from 20 participants of text deemed as relevant,
%  which among others, contain frames about required events, obligations, actions evoking system calls or executing some procedure.
% Given how these frames capture key factors used to understand a sentence's meaning
% and their prominence in relevant text, 
% we argue that semantic properties can enhance or complement the identification of task-relevant text.



\clearpage

% \subsubsection{Summary}


