

\section{Contributions}
\label{cp1:contributions}


The work presented in this thesis 
aims to improve how developers locate task-relevant information and thus, assist them in making more informed decisions related to their task.
Contributions that arise from this work are divided in three main categories, namely 
empirical studies, techniques, and corpora.



% ---------------------------------------------------------------------------------------

\paragraph{\textbf{Empirical Studies.}} 

It reports on two empirical studies for supporting a developer's discovery of task-relevant information:

\begin{itemize}

    \item A first study characterizes how task-relevant text appears across a variety of natural language artifacts pertinent to six software tasks; 

    \item A second study addresses whether 
    the text automatically identified by semantic-based techniques assist a software developer while they work on a task; this study provides empirical evidence on how a tool that automatically identifies 
    text relevant to a task assist developers complete the task-at-hand.
\end{itemize}


% ---------------------------------------------------------------------------------------


\paragraph{\textbf{Techniques.}} 

It introduces six possible techniques that incorporate the semantics of words and sentences for identifying task-relevant text in software artifacts, where:
    
\begin{itemize}
    
    \item it reports on the precision and recall of semantic-based techniques for the identification of text that human annotators deemed relevant to tasks associated with Android development; and
    \item it shows that semantic approaches have recall comparable to state-of-the-art approaches
    tailored specifically to certain kinds of artifacts.
\end{itemize}

% ---------------------------------------------------------------------------------------

\paragraph{\textbf{Datasets.}} 

It presents three different datasets that can be used for replication purposes and future research in the field, namely:
    
\begin{itemize}
    \item \acs{DS-synthetic} produced as part of our study on the consistency of text relevant to a task provides a unique corpus of 20 natural language artifacts associated
    with open-source projects that includes annotations from 20 participants of text deemed as relevant to six information-seeking tasks;
    
    \item \acs{DS-android} is a dataset with 50 Android tasks and associated textually-based artifacts 
    that we produced to evaluate the semantic-based techniques that we assess for the automatic identification of  task-relevant text;

    \item \acs{DS-python} is a by product of our empirical evaluation of the impact of tools that assist a developer's discovery of task relevant information.
    It contains three tasks related to well-known Python libraries and it includes annotations from 24 participants that indicated what text assisted them in writing each task's solution.
\end{itemize}