%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

\chapter{Acknowledgments}



I cannot express how much I am grateful for my supervisor, Gail Murphy. I feel incredibly privileged to have been supervised by someone so respectful, attentive, and inspiring. Thank you. 

I am equally grateful for all the support my family and my partner, Lisley Siqueira, provided me over the last six years. Moving to an entirely new country and starting our life together was a rollercoaster, yet it was a journey full of love, empathy and self-discovery. 

I am thankful to my supervisory committee, Reid Holmes and Muhammad Abdul-Mageed, for all their support and feedback over the last years. Their curiosity encouraged me to explore and learn many new things. I am also thankful to the members of my examining committee, Luanne Sinnamon, Alexander Summers, and Christina von Flach, for their time and effort in reading my thesis and providing insightful feedback. 

I am indebted to many of the friends and colleagues I made at the University of British Columbia, the Software Practices Lab, the Library Research Commons, the Oakridge Adventist Church, and the Vancouver DnD Collective. Many thanks to old-time friends who kept in touch despite being spread across the globe. I cannot name all of you, but I want to thank you all.


Thanks to all the Computer Science Department staff and Elise Vredenbregt for helping with hectic calendars. I would also like to acknowledge the Natural Sciences and Engineering Research Council of Canada for supporting this work. 


\begin{flushright}
Arthur Marques

October 2022
\end{flushright}


\clearpage

\thispagestyle{empty}
\vspace*{\fill}
\begin{flushright}
\emph{To my partner, Lisley Siqueira}
\end{flushright}
\vspace*{\fill}




\clearpage
\thispagestyle{empty}
\vspace*{\fill}

\begin{flushright}
    \emph{Hoje longe, muitas l\'egua}

    \emph{Numa triste solid\~ao}

    \emph{Espero a chuva cair de novo}

    \emph{Pra mim vortar' pro meu sert\~ao}

    --- Asa Branca, song by Luiz Gonzaga
\end{flushright}
\vspace*{\fill}

\clearpage