\setcounter{chapter}{1}


\chapter{Related Work}
\label{ch:related-work}




Performing a task on a software system, like fixing a bug
or adding a feature, typically requires a developer to consult
a number of different kinds of artifacts, such
as API documentation, bug reports, community forums
and web tutorials. 
Such natural language artifacts are produced on a 
continuous basis~\cite{Rastkar2013t} 
and locating the documents of interest for a task
is not trivial. 
To better understand this activity, 
many software engineering researchers 
have studied  a developer's information foraging process~\cite{Pirolli1999}
providing theories on how a developer searches for pertinent information
and proposing approaches to help this activity.
In Section~\ref{cp2:foraging},
we provide a general overview of background information on 
information foraging theory and 
then, in Section~\ref{cp2:foraging-tools}, we detail tools and approaches that 
assist  developers in finding artifacts pertinent their task.



Once a developer locates pertinent
software development artifacts, 
they must still identify \textit{within} these documents 
the fraction of text relevant to the task-at-hand.
To assist this activity, software engineering researchers have made use of the natural language
text appearing in different kinds of artifacts  in many different ways.
Many of the approaches that
use this text rely on lexical and syntactic properties of the text. 
In Section~\ref{cp2:artifact-approaches}, we review various studies that have been taken using these approaches,
honing in on studies that help identify text relevant to a task-at-hand.
More recently, researchers have also started to use semantic approaches; 
in Section~\ref{cp2:artifact-semantics} we 
provide an overview of these approaches to provide background of
how semantics can be useful to support software development activities.



\clearpage



\input{sections/cp2/theory}
% \input{sections/cp2/finding-artifacts}
% \input{sections/cp2/artifact-approaches}
% \input{sections/cp2/artifact-semantics}