\setcounter{chapter}{5}


\chapter{Evaluating Text Automatically Identified}
\label{ch:assisting}

\gcm{It would be better if the title was more aligned
with the earlier chapters. Maybe something like "Evaluating an Automated Approach to Task-Relevant Text Identification"}

\gcm{It would be helpful if you can link more directly to the earlier chapters as in ... In the last chapter, we showed that semantic-based approaches can help identify text in artifacts relevant to a task. In this chapter, we consider whether these approaches can assist a software developer...}

Previously, we have compared different semantic-based techniques for automatically identifying text in an artifact that is of potential relevance to a software task.
Although, such a comparison answered whether semantic-based approaches can identify text that humans deem relevant,
it did not address whether 
the text automatically identified  
can assist a software developer while they \textit{work} on a task.



This chapter describes the results of a controlled experiment that 
investigated how a  semantic-based technique from Chapter~\ref{ch:identifying} can impact a developer's work. 
With this experiment, we report qualitative and quantitative  data obtained from 24 participants who attempted Python
programming tasks when assisted (or not) by a tool that automatically highlights text that it determines as relevant to the participant's task. 


We start by outlining the evaluation approach  (Section~\ref{cp6:method}). We then
detail experimental procedures  (Sections~\ref{cp6:experiment})before reporting
results from the experiment 
Section~\ref{cp6:results}.
Section~\ref{cp6:summary} concludes the chapter.

% ---\textit{BERT with no filters}---

\clearpage







% We conclude this chapter presenting threats to the validity of our experiment (Section~\ref{cp6:threats}) and 
%  summarizing our key findings (Section~\ref{cp6:summary}).




\input{sections/cp6/motivation}
\input{sections/cp6/experiment}
\input{sections/cp6/results}
\input{sections/cp6/summary}

\gcm{Sorry if I missed it but do you outline the number of artifacts and type of artifacts per task?}



% \art{I'm trying to set results in a manner similar to how we did in the ICPC paper---present an overview of what we evaluate in the section, describe the method of evaluation and then, the results.}


% \input{sections/cp6/summary}

